A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-07 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
Add a reference to next-generation identity federation

The existing technologies leveraged by identity federations, e.g., the
Security Assertion Markup Language (SAML), have not supported non-web
applications historically. There is momentum within the wider community
to develop next-generation identity federations that natively support a
wider range of clients. In the meantime there are several viable interim
solutions that are able to provision users with the token required to
access a service (such as X.509) transparently, translated from their
home organisation identity.

>>>>

The existing technologies leveraged by identity federations, e.g., the
Security Assertion Markup Language (SAML), have not supported non-web
applications historically. There is momentum within the wider community
to develop next-generation identity federations~\cite{OICFederation}
that natively support a
wider range of clients. In the meantime there are several viable interim
solutions that are able to provision users with the token required to
access a service (such as X.509) transparently, translated from their
home organisation identity.
